% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Evaluation}

% Please do not change the subtitle
\subtitle{COMP120 - Evaluation}

% Please put your student number in the author field
\author{James (JH182233) 1506530}

\begin{document}

\maketitle

\section{Time Keeping}

Over the course I found that I kept getting distracted from the course projects. For me the most significant issue was not practising the practical side of programming, at first I felt lost, this might be due to the fact that i had been out of education for an extended period of time. Unlike being employed, education requires you to demonstrate your own timekeeping more strictly than employment would. Having experienced university I now realise I have not sufficiently developed my ability to use my free time efficiently. I will schedule my time and note it to keep track of my progress, by creating a daily timetable that will account for programming practice and leisure.

\section{Communication}

In class i have seen a great lack of communication, for me its mainly my pride that is the cause. Previously in my old employment I know that being in charge meant that I had to communicate with the staff in order to work efficiently. Initially I felt uncomfortable asking questions to anyone. As time went on though I became comfortable talking to the tutors about my issues. Having discussed my position in the class with the tutor I now realise that i wasn't the only one. Through this I have significantly improved my ability to communicate with my peers. This means that 

\section{Reading}


\bibliographystyle{ieeetran}
\bibliography{comp110_architecture}

\end{document}
